\addcontentsline{toc}{section}{Abstract}
\section*{Abstract} \label{sectionAbstract}

% When writing an abstract, bare in mind an abstract is a short descriptive summary of your thesis. The number of words accepted might vary e.g. 200-250 words. An MS thesis abstract need not exceed two pages. Abstracts are typically written last although they are the most important part of the thesis. They should have a little bit of everything: the background, the scope of your project, the purpose, findings and conclusions. An abstract is neither paragraphed nor cited. It should not be written as a literature review or a discussion of results. In a simplistic manner, your abstract, in a few words, should answer the questions: why should we care about your research; how did you get your results; what did you learn, find, create, invent; and finally what do your results imply?

% State the problem.
Some software engineering projects fail to evolve, making them obsolete. When we build new software solutions, we consider several categories during planning: cost, time-to-deliver, and sometimes to a smaller extent, quality. Though quality can be a factor we consider when planning a project, it is a complex attribute to understand and measure.
% Say why this problem is interesting.
We care about quality, as it can impact the longevity of a project. Low-quality software can be complicated to enhance and evolve. Software that fails to evolve will fail to generate user engagement, leading to revenue loss.
Many tools are available for enforcing standards, some built into integrated development environments (IDEs) (like Visual Studio Code) and others as third-party linter tools. Two such tools are Pylint and Radon, which can analyze Python projects. In particular, we will focus on the refactor violations noted in Pylint and Radon's code reports, as these warnings can lead us to code smells.
% Say what my solution achieves.
We review some projects and resources to understand the correlation between software structure quality and its impacts on a system's evolving ability. For example, we find that our reviewed projects have a low count of refactoring messages and middle to high maintainability indexes, indicating that these measurements may help estimate the quality of a system.
% Say what follows from my solution.
With this understanding, we explore ways to improve the evolution of a software system through tools and suggestions.
